
\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=0.75in]{geometry}

\usepackage[english]{babel}

\hyphenation{Some-long-word}
\usepackage{mdwlist}
%\usepackage{multicol}
\usepackage{relsize}

\usepackage{hyperref}  
\usepackage{xcolor}
\definecolor{dark-blue}{rgb}{0.15,0.15,0.4}
\hypersetup{colorlinks,linkcolor={dark-blue},citecolor={dark-blue},urlcolor={dark-blue}}

\usepackage{tgpagella}
\usepackage[expansion,protrusion]{microtype}


\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\xspaceskip7pt

\newcommand\maintitle[3]{\vbox to 0pt{\hfill\scriptsize\color{gray} #3}\vspace{-0.4em}\noindent{\LARGE \textbf{#1}}\ \ \ \emph{#2}}

\newcommand*\roottitle[1]{\subsection*{#1}\vspace{-0.3em}\nopagebreak[4]}

\newcommand*\acr[1]{\textscale{.85}{#1}}

\newcommand*\bull{\raisebox{-0.365em}[-1em][-1em]{\textscale{4}{$\cdot$}}}
\newcommand*\sbull{\ \ \bull \ \ }

\newlength{\newparindent}
\addtolength{\newparindent}{\parindent}

\newlength{\doubleparindent}
\addtolength{\doubleparindent}{\parindent}
\addtolength{\doubleparindent}{\parindent}

\newlength{\tripleparindent}
\addtolength{\tripleparindent}{\parindent}
\addtolength{\tripleparindent}{\parindent}
\addtolength{\tripleparindent}{\parindent}

\newenvironment{indentsection}%
{\begin{list}{}%
  {\setlength{\leftmargin}{\newparindent}\setlength{\parsep}{0pt}\setlength{\parskip}{0pt}\setlength{\itemsep}{0pt}\setlength{\topsep}{0pt}}%
}
{\end{list}}

% headerrow command, used for a new employer
\newcommand{\headedsection}[3]{\nopagebreak[4]\begin{indentsection}\item[]\textscale{1.1}{#1}\hfill#2#3\end{indentsection}\nopagebreak[4]}

% subheaderrow command, used for a new position
\newcommand{\headedsubsection}[3]{\nopagebreak[4]\begin{indentsection}\item[]\textbf{#1}\hfill\emph{#2}#3\end{indentsection}\nopagebreak[4]}

% body text (indented)
\newcommand{\bodytext}[1]{\nopagebreak[4]\begin{indentsection}\item[]#1\end{indentsection}\pagebreak[2]}

% \vspace variaties
\newcommand{\breakvspace}[1]{\pagebreak[2]\vspace{#1}\pagebreak[2]}
\newcommand{\nobreakvspace}[1]{\nopagebreak[4]\vspace{#1}\nopagebreak[4]}

% \spacedhrule a horizontal line with some vertical space before and after it
\newcommand{\spacedhrule}[2]{\breakvspace{#1}\hrule\nobreakvspace{#2}}

% \inlineheadsection command, used for a new employer
\newcommand{\inlineheadsection}[2]{\begin{basedescript}{\setlength{\leftmargin}{\doubleparindent}}\item[\hspace{\newparindent}\textbf{#1}]#2\end{basedescript}\vspace{-1.7em}}

% apo command, for an apostrophe that looks good on old style nums
\newcommand{\apo}{\raisebox{-.18ex}{'}{\hspace{-.1em}}}

% non space that allows line breaks
\newcommand*{\nsp}{\hskip0pt}

% Header 1 with no further instructions
\newcommand{\headerone}[1] {\textscale{1.2}{\textbf{#1}}\vspace{0.7em}\nopagebreak[4]}

% Header2 with no further instructions
\newcommand{\headertwo}[1]{\nopagebreak[4]\textbf{#1}\nopagebreak[4]}

% Header 3, inline
\newcommand{\headerthreeinline}[2]{\vspace{-2.0em}\begin{basedescript}{\setlength{\leftmargin}{\tripleparindent}}\item[\hspace{\tripleparindent}\textbf{#1}]#2\end{basedescript}\vspace{0.1em}}


\begin{document} 
\sloppy  

%%%%%%%%%%% Name and contact
\maintitle{Ian Smith}{}{}

\nobreakvspace{0.3em}  

\noindent\href{mailto:ismith1024@gmail.com}{ismith1024\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}1 613-601-0541
\\
208-323 Winona Ave\sbull
Ottawa, Ontario, Canada\sbull
\acr{K1Z 5H3}\\
    {\href{https://github.com/ismith1024}{github.com/ismith1024}}


\spacedhrule{0.9em}{-0.4em}

%%%%%%%%%%%% Summary

\roottitle{Summary} 

%\vspace{-1.3em}  
%\begin{multicols}{2}  
\noindent
%\begin{itemize}
I currently lead a research team within Intertek's Kanata office which enables the Global Restricted Substances (\acr{GRS})
group conduct supply chain audits and risk analysis as part of conformity assessment against chemical regulations.\\

\noindent During my time with this role I have harmonized service offerings and re-focused operations from ``boutique'' consulting services to data-driven, automated analytics.
This has contributed to \acr{GRS}'s status as at or near Intertek's worldwide leader in profitability and growth over the last year.  Specific technologies include use of machine learning, data mining, data integration, and software engineering, as well as maintaining the team's research knowledge base.\\

\noindent As my role has transitioned from subject-matter expertise to data management tool development, I have completed a part-time \acr{B.C.S.} at Carleton University's School of Computer Science on my own initiative, and achieved a grade point average of 11.75 out of 12.\\

%\end{itemize}
%\end{multicols}


\spacedhrule{0em}{-0.4em}

%%%%%%%%%%%% Professional experience

\roottitle{Professional Experience}

    \headedsection  
    {\href{http://www.intertek.com}{Intertek}}
    {\textsc{Global Restricted Substances --- Ottawa, Canada}} {
    \headedsubsection
        {Engineer}
        {October 2009 -- present}
        {\bodytext{Intertek is a global auditing, testing, and certification service provider. 
Designed and implemented a configurable risk analysis platform for worldwide chemical regulatory compliance.
Mine and analyze data to keep up to date on enforcement and risk trends.  Automate business processes.  Mentor junior team members. }}
}

\headedsection  
    {\href{http://www.intertek.com/news/2007/10-23-acquisition-ageus/}{Ageus Solutions}}
    {\textsc{Ottawa, Canada}} {
    \headedsubsection
        {Engineer}
        {January 2005 -- October 2009}
        {\bodytext{Ageus Solutions was a successful independent consulting startup which was integrated into Intertek Health and Environmental after acquisition.  One of the founders of the company.  Served on board of Directors and as a corporate officer.  Responsible for legal due diligence during \acr{M\&A}.  Designed core analytical services and directed team of regulatory researchers.}}
}

\headedsection
    {\href{http://www.bce.ca/news-and-media/releases/show/nortel-networks-creates-high-performance-optical-components-business-unit}{Nortel Networks}}
    {\textsc{Optical Components --- Ottawa, Canada}} {
    \headedsubsection
       {IC Designer}
        {June 2000 -- December 2004}
        {\bodytext{ The former Nortel Optical Components Group designed and fabricated \acr{GaAs ICs} for use in optical long haul equipment.  
        Analyzed integrated circuits and discrete semiconductor devices for root-cause of failure.  
        Assembled and ran laboratory at minimal cost during downsizing. 
        Experimentally demonstrated recurring failure mechanisms.  Advised manufacturing operations to implement corrective action.}}
}


\spacedhrule{0.5em}{-0.4em}

%%%%%%%%% Education

\roottitle{Education}

\headedsection
    {\href{http://carleton.ca}{Carleton University}}
    {\textsc{Ottawa, Canada}} {
    \headedsubsection
        {Bachelor of Computer Science, Honors}
        {2018}
        {\bodytext{With High Distinction.  Data management, \acr{AI}, and software engineering.  
        Web and mobile application development. Computer Vision.  
        Awarded Senate Medal for Outstanding Academic Achievement }}
}

\headedsection
    {\href{http://www.umanitoba.ca}{University of Manitoba}}
    {\textsc{Winnipeg, Canada}} {
    \headedsubsection
        {B.Sc. (Electrical Engineering)}
        {1999} 
        {\bodytext{Focused on microelectronics and \acr{VLSI} design. Acquired proficiency in \acr{IC} design tools, statistics and mathematics, \acr{MATLAB}, and \acr{C++}. }} 
}

\spacedhrule{0.5em}{-0.4em}

\pagebreak
%%%%%%%%%%% Skills

\roottitle{Technical Skills}

    \inlineheadsection
    {Applications:} {Data mining, analytics, machine learning, business process automation, data integration, data cleaning, \acr{ETL}\\}
    \inlineheadsection
    {Languages:}{Java, \acr{SQL}.  Secondary experience with web development using \acr{HTML}, JavaScript (including jQuery), and hosting \acr{REST} server. Shell scripts including \acr{BASH}, PowerShell. \acr{C++}\\} 
    \inlineheadsection
    {Academic experience only:}{\acr{R}, Swift, Python, \acr{C}, Android, \LaTeX } 
  
\spacedhrule{1.5em}{-0.4em}

%%%%%%%%%%%% Projects
\roottitle{} 
\headerone{Recent Professional Projects}

   \headertwo{Risk Analysis System} \\        
   \headerthreeinline{Purpose: }{ Enables the business to perform conformity assessment and risk analysis based on supply-chain data.  The regulatory requirements, substances, and risk assessment criteria are abstracted and can be configured as new uses are required.
    System applies elements of \acr{AI} (machine learning and natural-language processing) to assist with decision-making that would not be possible using a conventional, rule-based, approach.}
    \headerthreeinline{Technology: }{Object-oriented design,  Machine Learning, Java, \acr{SQL}, \acr{JSON}}
    \headerthreeinline{Personnel: }{Two developers} 
    
  \headertwo{Data Integration} \\        
   \headerthreeinline{Purpose: }{Allows for the use of third-party partner or client data.  Integrates engineering and operational databases.  Part of this exercise included writing the data interchange specification used by clients and business partners.  %Built interface to stream data from provider's \acr{REST} \acr{API}.
   }
    \headerthreeinline{Technology: }{\acr{SQL}, Java }
    \headerthreeinline{Personnel: }{Multiple development teams across Intertek and business partner.} 
   
   \headertwo{Regulatory Research Tools} \\        
   \headerthreeinline{Purpose: }{Assists research team by automatically mining regulatory enforcement data from regulatory bodies.  Extracts structured data from text, and performs statistical analysis.}
    \headerthreeinline{Technology: }{\acr{SQL}, 
     Java, Text mining, Multithreaded network communications, \acr{AJAX} }
    \headerthreeinline{Personnel: }{Four researchers} 
    
    \headertwo{Web Dashboard (Middleware Layer)} \\        
   \headerthreeinline{Purpose: }{Demonstration of an interactive portal which would allow clients to view status and preliminary findings of conformity projects in real-time.  This project is on hold pending data center's implementation of API specification.}
    \headerthreeinline{Technology: }{\acr{REST}, Javascript, jQuery, \acr{SQL}, Node.js, \acr{JSON} }
    \headerthreeinline{Personnel: }{Solo effort}     
    
%%%%%%%%%%%%%% ACADEMIC PROJECTS
\spacedhrule{1.5em}{-0.4em}


%%%%%%%%%%%% Projects
\roottitle{} 
\headerone{Academic Projects}

   \headertwo{Honors Project} \\        
   \headerthreeinline{Purpose: }{ Uses Natural Language Processing to extract product structure and composition from free text obtained from industrial designs.  Implemented in \acr{C++}.}
    \headerthreeinline{Technology: }{Natural Language Processing}
    

   \headertwo{Securities Analysis} \\        
   \headerthreeinline{Purpose: }{ Uses multi-layer perceptron and Kohonen map to predict equity returns.  This project is distinguished from typical stock market analysis in that it attempts to make long-term predictions on the basis of fundamental, rather than technical, analysis (as emphasized by the ``Value'' style of investing).
   Daily economic and market data dating back to the mid 1990's is analyzed.}
    \headerthreeinline{Technology: }{Neural Networks, Data Integration}
    


\spacedhrule{1.5em}{-0.4em}

\vfill  
{\footnotesize Last updated on \today}
\end{document}
